### 2013-08-03 pystruct/paper.tex
minor fixes, images
use natbib citation commands everywehere.

% Definitions of handy macros can go here

%\DeclareMathOperator*{\argmax}{arg\,max}
%\DeclareMathOperator*{\argmin}{arg\,min}

%\newcommand{\dataset}{{\cal D}}
%\newcommand{\fracpartial}[2]{\frac{\partial #1}{\partial  #2}}

%\newcommand{\x}{\checkmark}
%\renewcommand{\o}{$\times$}
%\newcommand{\pystruct}{{\sc PyStruct} }

@@

Structured prediction can be defined as making a prediction $f(x)$ by maximizing an
compatibility function $g$ between an input $x$ and the possible labels
$y$~\cite{nowozin2011structured}. Most current approaches use linear functions,
leading to:
\begin{equation}\label{eq:main_equation}
    f(x) = \argmax_{y \in \mathcal{Y}} \langle \theta, \Psi(x, y) \rangle 
\end{equation}
Here, $y$ is a \emph{structured} label in the sense that it is more complicated than a single
output class. Examples include predicting a label for each word in a sentence, or predicting
a label for each pixel in an image.
Learning structured prediction means learning the parameters $\theta$ from training data
$(x_1, y_1), \dotsc, (x_n, y_n)$.

@@

\bottomrule
\end{tabularx}
\vspace{-3mm}
    \caption{Comparison of structured prediction software packages. CP stands
for cutting plane optimization of SSVMs~\cite{joachims2009cutting}, SG for
online subgradient optimization of SSVMs~\cite{ratliff2007online}, LV for
latent variable SSVMs~\cite{yu2009learning}, ML for maximum likelihood
training, Chain for chain-structured models
with pairwise interactionsr, Graph for arbitrary graphs with pairwise
interactions, and LDCRF for latent dynamic CRF~\citep{morency2007latent}.\label{table:comparision}}
\end{table}

>>>>

@@

Structured prediction can be defined as making a prediction $f(x)$ by maximizing an
compatibility function $g$ between an input $x$ and the possible labels
$y$~\citep{nowozin2011structured}. Most current approaches use linear functions,
leading to:
\begin{equation}\label{eq:main_equation}
    f(x) = \argmax_{y \in \mathcal{Y}} \langle \theta, \Psi(x, y) \rangle 
\end{equation}
Here, $y$ is a \emph{structured} label in the sense that it is more complicated than a single
output class. Examples include predicting a label for each word in a sentence, or predicting
a label for each pixel in an image.
Learning structured prediction means learning the parameters $\theta$ from training data
$(x_1, y_1), \dotsc, (x_n, y_n)$.

@@

\bottomrule
\end{tabularx}
    \caption{Comparison of structured prediction software packages. CP stands
for cutting plane optimization of SSVMs~\citep{joachims2009cutting}, SG for
online subgradient optimization of SSVMs~\citep{ratliff2007online}, LV for
latent variable SSVMs~\citep{yu2009learning}, ML for maximum likelihood
training, Chain for chain-structured models
with pairwise interactionsr, Graph for arbitrary graphs with pairwise
interactions, and LDCRF for latent dynamic CRF~\citep{morency2007latent}.\label{table:comparision}}
\end{table}
